Online Balanced Graph Partitioning: Optimizations for Large Clusters

### 2020-05-06 paper/disc20clustering.tex

	To keep \OPT's cost low, we end extending ground sets prematurely --- while there are still $\ell+1$ alone nodes (i.e., neglecting two last ground set expansions).
	At the moment of termination, there exist two alone nodes that originate from the same cluster (as we have $\ell+1$ alone nodes and $\ell$ clusters).
	We denote these two nodes by $x^*$ and $y^*$.

>>>>

	To keep \OPT's cost low, we end extending ground sets prematurely --- while there are still $\ell+1$ alone nodes (i.e., neglecting two last ground set expansions).
	Consider \ALG's configuration after the last expansion.
	Among $\ell+1$ alone nodes there must exist a pair that originates from the same cluster (we have $\ell$ clusters). 
	We denote these two nodes by $x^*$ and $y^*$.
